\documentclass[11pt]{article}

\usepackage[a4paper,margin=2.4cm]{geometry}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

\newcommand{\impmodel}{IMP--MiT-B3 U-Net}
\newcommand{\cleanv}{Clean-v3}

\title{Evidence-Bounded Comparison of MiT-B3 U-Net and nnU-Net for Skin Lesion Segmentation}
\author{Nguyễn Trần Minh Quân \and Nguyễn Đức Lân}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
Reliable dermoscopic lesion segmentation requires more than a high overlap score: dataset leakage, image-quality variation, boundary errors, and post-hoc model selection can each invalidate an apparently strong result. We report an evidence-bounded comparison built after auditing the IMP project's data lineage. The leakage-audited \cleanv{} manifest contains 2,869 images split into 2,008 training, 431 validation, and 430 sealed test images with no detected cross-split identity-group overlap. On the already-opened, adaptively used \cleanv{} development-validation partition, the project's preprocessing-aware MiT-B3 U-Net control obtained robust Dice 0.8959 and boundary F1 0.4145, while a raw-RGB nnU-Net v2 model obtained robust Dice 0.9019 and boundary F1 0.4369. These are selection-optimistic, single-run point estimates under an older geometry contract; the protected test partition was not opened, so they do not establish statistical superiority or state of the art. We additionally analyze a controlled three-seed train-screen experiment in which a saliency-constrained active-contour mask was supplied as a fourth channel. Contrary to the motivating hypothesis, the contour channel changed seed-and-view-averaged robust Dice by $-0.0313$ (95\% split-group cluster-bootstrap confidence interval $[-0.0491,-0.0156]$, conditional on the three selected seeds). The boundary-F1 change was $-0.0147$ ($[-0.0308,0.0010]$). The result rejects this implementation before protected evaluation but does not quantify uncertainty over seed selection. The report demonstrates a useful outcome even without a positive model claim: leakage-aware evidence classification, strong-baseline comparison, and documentation of a negative ablation can prevent an internal benchmark from becoming an unsupported leaderboard claim.
\end{abstract}

\noindent\textbf{Keywords:} skin lesion segmentation; dermoscopy; nnU-Net; MiT-B3; data leakage; robustness; active contour; negative results

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_data_protocol}
\input{sections/04_methods}
\input{sections/05_experiments}
\input{sections/06_results}
\input{sections/07_discussion}
\input{sections/08_limitations_ethics}
\input{sections/09_reproducibility}
\input{sections/10_conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
