\section{Related Work}

\subsection{Biomedical segmentation architectures}

U-Net established the encoder--decoder template with skip connections that remains central to biomedical segmentation \citep{unet2015}. Attention U-Net and UNet++ subsequently introduced attention gating and nested skip pathways \citep{attentionunet2018,unetplusplus2018}. Transformer encoders provide a complementary mechanism for multiscale contextual modeling. SegFormer introduced a hierarchical Mix Transformer (MiT) encoder and a lightweight all-MLP decoder for semantic segmentation \citep{segformer2021}. The IMP implementation uses a MiT-B3 encoder inside the U-Net decoder supplied by \texttt{segmentation-models-pytorch}; it is therefore not an exact reproduction of the original SegFormer decoder. We retain the historical project label in artifact identifiers but use ``MiT-B3 U-Net'' when describing the implemented architecture.

nnU-Net takes a different position: it treats preprocessing, architecture configuration, training, inference, and postprocessing as an integrated self-configuring pipeline \citep{nnunet2021}. This makes nnU-Net a stronger comparator than a weak manually configured U-Net. Lesion-specific systems such as EGE-UNet target efficient multiscale aggregation \citep{egeunet2023}, while DermoSegDiff investigates boundary-aware diffusion modeling \citep{dermosegdiff2023}. These methods motivate broader architecture panels, but only models evaluated under a common leakage-safe protocol can support direct ranking in this report.

\subsection{Appearance normalization and robustness}

Dermoscopy pipelines commonly attempt to normalize local contrast and color variation. Contrast-limited adaptive histogram equalization enhances local luminance contrast while limiting amplification \citep{zuiderveld1994clahe}. Shades-of-Gray color constancy estimates scene illumination through a Minkowski-norm generalization of Gray World \citep{finlayson2004shades}. Such operations can improve visibility but can also suppress weak boundary evidence or amplify noise. The relevant causal question is not whether a processed image appears clearer, but whether a fixed operation improves a matched model under controlled corruptions.

\subsection{Saliency and active contours}

Regional saliency methods use color, texture, spatial layout, and background connectivity to estimate lesion support. Supervised saliency and background-detection approaches have been studied directly for dermoscopic segmentation \citep{jahanifar2019saliency,ahn2017background}. Active-contour and level-set methods then refine a coarse support using image gradients and shape evolution; distance-regularized level-set evolution is a representative formulation \citep{li2010drlse}. Loop206 combines a learned regional saliency map with a morphological geodesic active contour. It is paper-inspired engineering, not an exact reproduction of any cited method.

\subsection{Leakage and metric discipline}

Subject overlap can make held-out performance dependent on information already seen during training. Leakage is especially damaging when repeated images, lesions, or patients appear across nominal partitions \citep{kapoor2023leakage}. Evaluation choices can likewise change conclusions: overlap, boundary, and distance metrics measure different failure modes and require explicit geometry, threshold, and empty-mask policies \citep{maierhein2024metrics}. We therefore report Dice and IoU together with precision, recall, boundary F1, HD95, and ASSD where valid, and we bind every claim to a dataset version, partition, metric contract, and evidence class.
