\section{Limitations and Ethics}

The main architecture comparison has six substantial limitations. First, its validation partition was used adaptively for development, checkpoint or model selection, and promotion decisions, so its point estimates may be selection-optimistic. Second, it uses validation rather than protected test evidence. Third, each architecture has only one recorded run, so stochastic variance is unknown. Fourth, Loop192 probabilities were generated at $256\times256$ and resized to a $384\times384$ metric canvas under an older contract. Fifth, the compared systems differ in multiple training and architecture variables, preventing component-level causal attribution. Sixth, paired per-case predictions and the complete original dataset were unavailable in the initial Windows rescue environment, preventing metric-v2 recomputation during manuscript framing.

Loop206 improves causal control but remains a small train-screen study. It contains 76 held-out training groups, three selected seeds, and three corruption conditions. The bootstrap resamples groups after averaging those seeds and views; it does not estimate variability over alternative seed selections. Its confidence interval supports rejection of the tested contour channel on this protocol, not universal rejection of active contours, saliency, or fourth-channel models. The protected validation, test-v3, and PH2 cohorts were intentionally not opened after failure.

The live lane has historical/superseded Task 4 operational observations: sidecar/Gradio inference, desktop and mobile browser checks, fail-closed oversized input, retry/recovery, and an ephemeral Cloudflare public GET. The current canonical Task 4 browser/mobile/Cloudflare packet remains \texttt{unverified/blocked}; these bounded historical observations are not current-release acceptance evidence and do not establish end-to-end acceptance. It remains illustrative only: it has no ground truth, accuracy evaluation, canonical release receipt, or original-runtime equivalence evidence. In addition, one bundled public sample exceeds the pinned 16 MiB request contract. Repeated reconstructed nnU-Net inference drifted despite matched bindings, so determinism remains blocked. The recorded ordered shutdown closed the owned ports but exited 5; browser, tunnel, shutdown, and determinism observations do not promote a scientific result.

The source datasets are dermoscopic image collections governed by their respective ISIC challenge terms. Code and derived evidence can be shared subject to review, but raw data and model weights are not redistributed in the repository. Uploaded website images are processed ephemerally and are not retained in logs. The demonstration produces segmentation masks, not diagnoses. It has not undergone prospective, subgroup, fairness, calibration, security, or clinical validation and must not be used for medical decisions.
