\section{Reproducibility}

The rescue package binds headline results to a canonical JSON evidence registry. Each source report is identified by a project-relative path and SHA-256. The registry records the dataset version, partition, evidence class, metric contract, seed count, headline values, confidence intervals, and limitations used in the generated paper tables; it is not the source of every implementation or resource parameter. Paper tables are generated from that registry rather than transcribed manually. Registry-only verification establishes semantic and hash consistency, not full experiment reproduction.

Prospective RQ1-v2 index/integrity admission remains \texttt{blocked}. The historical source-report audit is retained as recorded evidence rather than promoted into a new prospective admission claim.

\subsection{Protocol and resource provenance}

The source reports used for Loop191 and Loop192 record the $384\times384$ IMP setup, the raw-RGB $256\times256$ nnU-Net setup, and the historical $384\times384$ metric canvas. However, the cited Loop191 and Loop192 configuration files, their implementation modules, the inherited postprocessing module, and the compact source reports are not tracked in this release. Their numeric settings are therefore source-report evidence available to the strict local audit, not a clone-runnable recipe supplied by this commit.

The tracked release does include the Loop205 regional-saliency module, the Loop206 active-contour module, and the seed-206 zero-channel control configuration. The other five Loop206 arm/seed configurations, preflight receipt, and final scientific report are not tracked in this release. The evidence registry binds the final report hash and headline deltas, while the operator-local report records 20 epochs, seeds 206/1206/2206, 308 fit groups, 76 holdout groups, three views, resource measurements, and the group-bootstrap definition. A fresh clone can validate these recorded claims and rebuild tables, but cannot re-run all six training jobs from tracked files alone.

The repository includes the demo model constructor, metric and evidence code, Loop205 regional saliency protocol, Loop206 active-contour implementation, one Loop206 control config, table builder, tests, and website source. Runtime data, additional experiment configs, checkpoints, probability caches, source reports, and large artifacts remain outside Git. The selected Loop206 control and candidate checkpoints are verified by SHA-256 at application startup.

The live comparison contract pins L206-control-s206 and the reconstructed L192-nnUNet-v2-raw-100ep runtime. The historical Task 4 resume report records loopback sidecar/Gradio work, fail-closed oversized input, retry/recovery, desktop 1440x900 and mobile 390x844 browser checks, and an ephemeral Cloudflare public GET. That report is not current-release acceptance evidence. Current-release browser, mobile/desktop visual, and tunnel status is \texttt{unverified/blocked}: \texttt{demo\_runtime/acceptance/imp.dual\_live.e2e.v1/20260722T233947051Z/acceptance.json} is \texttt{blocked\_missing\_prerequisite} and its browser/tunnel fields are intentionally absent; the Presenter S transcript also records browser rendering and desktop/mobile screenshots as unverified. No canonical live runtime receipt is present in this release. Ground truth is not loaded, and accuracy is not measured or claimed. Receipt eligibility is conditional on both arms succeeding against the same RGB input and emitting valid model, checkpoint, input, and mask bindings. Neither original-runtime equivalence nor a replay of an original Loop192 output is claimed.

\subsection{P1 rerun readiness}

P1 remains \texttt{BLOCKED}. An authorized verified Clean-v3 index and integrity report are unavailable; the recorded 2,008/431 counts are protocol metadata rather than verified identities. The release also lacks a real MiT-B3 tensor-state hash, six locked configs/runtime manifests/job receipts, and the associated experiment-input bindings. These missing artifacts prevent a new scientific rerun, leakage audit, or promoted P1 metric claim.

For arbitrary uploaded images, the candidate model requires a deployment saliency prior fitted only from the 308 Loop206 fit groups. Deployment is authorized only if the resulting contour generator reproduces all 76 frozen holdout clean contours byte-for-byte. If data identity, source hashes, model hashes, or contour parity fail, candidate upload inference remains disabled rather than using an approximate channel.

The recorded experiment hardware is an RTX 5060 Ti workstation with Python 3.12. Environment dependencies are locked with \texttt{uv}. An operator log states that a same-machine clean-clone simulation passed the portable workflow, but no tracked, commit-bound receipt was retained; this release therefore treats that execution as unverified. Physical execution on the RTX 4060 laptop, including a laptop CUDA receipt, remains unverified; no physical laptop execution is claimed.
